\thesistitle

### 2019-07-19 sections/conclusion.tex
Different set

\subsection{Running our experiments with a greater diversity of software projects}
\todo{TODO}

>>>>

\subsection{Running our experiments with a different set of software projects}
In our experiments we chose to use a GitHub based software corpus. This corpus contains a diversity of projects of many different sizes. We noticed that there is a lot of difference in the quality of these software systems: some systems had a lot of duplication and some did not have any duplication.

We think that there is value in running our experiments with different corpuses. We would, for instance, be interested in the results for industrial projects instead of open source software systems. We are curious to see whether the distributions are comparable, or whether they show large differences.

Furthermore, we think that there is value in running our experiments with a set of larger sized and more professionally developed open source systems. We noticed that in our corpus there were a lot of projects that have only few commits and contributors. We think it would be valuable to for instance perform our experiments with a set of larger open source systems, like the systems in the apache ecosystem.
